
\documentclass{curriculum-vitae}

\usepackage[english]{babel}

\name{John}
\surname{Doe}

\shortinfo{%
	\maillink{john.doe@example.com}%
	\sep%
	\phonelink{+12 345 6789012}%
	\sep%
	\weblink{\faGlobe}{johndoe.dev}{https://startpage.com} \\
	\weblink{\faLinkedin}{johndoe}{https://startpage.com}%
	\sep%
	\weblink{\faGithub}{johndoe}{https://startpage.com}%
	\sep%
	\weblink{\faMastodon}{@johndoe}{https://startpage.com}%
	\sep%
	\lastupdated%
}

\phrase{I am an experienced \textbf{mechanical engineer} with a passion for \textbf{computational methods} and \textbf{artificial intelligence}, particularly in the fields of \textbf{numerical simulations} and \textbf{machine learning applications} for engineering problems.}

\begin{document}

\cvhead

\cvsection{Academic Background}
\cvdatedentry{M.Sc. in Advanced Mechanical Engineering (GPA: 1.1, Top 1\%)}{Mar. 2022 - Sep. 2023}{%
	Obtained from \textit{Institute of Technology} \\
	Thesis: \textit{Computational Optimization for Structural Analysis} \inlinelink{pdf}{https://startpage.com}
}
\cvdatedentry{B.Eng. in Mechanical Engineering (GPA: 1.8, Top 10\%)}{Oct. 2018 - Mar. 2022}{%
	Completed at \textit{Institute of Technology} \\
	Thesis: \textit{Numerical Simulation of Advanced Materials} \inlinelink{pdf}{https://startpage.com}
}
\cvdatedentry{Higher Secondary Education (Abitur Equivalent)}{Jun. 2018}{%
	Graduated from \textit{XYZ Science Academy} \\
	Specialized in Mathematics, Physics, and Computer Science.
}

\cvsection{Honors \& Awards}
\cvdatedentryshort{Outstanding Research Award}{2021}{%
	Recognized for innovative contributions in research. \inlinelink{article}{https://startpage.com}
}

\cvsection{Professional Experience}
\cvdatedentry{Institute of Technology, Research Scientist}{Sep. 2023 - Present}{%
	Developing novel computational approaches for analyzing complex mechanical structures with non-linear material behavior.
}
\cvdatedentry{Institute of Technology, Research Assistant}{Apr. 2022 - Sep. 2023}{%
	Worked on software development for high-precision finite element simulations and computational material modeling.
}
\cvdatedentry{Tech Firm, Machine Learning Engineer Intern}{Apr. 2021 - Mar. 2022}{%
	Developed and optimized predictive maintenance models using deep learning algorithms for industrial applications.
}

\cvsection{Teaching Experience}
\cvdatedentry{Institute of Technology, Numerical Methods \& Structural Analysis}{Sep. 2023 - Present}{%
	Teaching assistant for graduate courses in computational mechanics and numerical analysis.
}
\cvdatedentry{Institute of Technology, Engineering Fundamentals Course}{Winter 2022}{%
	Co-led an introductory engineering course, providing hands-on training in design and analysis.
}

\cvsection{Publications \& Presentations}
\cvdatedentry{Presentation at International Symposium on Computational Engineering \inlinelink{slides}{https://startpage.com} \inlinelink{certificate}{https://startpage.com}}{Jul. 2024}{%
	Multi-scale finite element methods for elastoplastic structures, \textit{J. Doe, A. Smith, B. Johnson}
}

\newpage
\cvsection{Major Projects}
\cventry{Development of High-Order Simulation Framework \inlinelink{code}{https://startpage.com}}{%
	Created an advanced finite element library supporting adaptive meshing techniques and computational efficiency improvements.
}

\cvsection{Extracurricular Engagement}
\cvdatedentry{Formula Racing Team Member \inlinelink{team}{https://startpage.com}}{Oct. 2019 - Feb. 2023}{%
	Involved in vehicle dynamics optimization, simulation, and mechanical component design.
}

\cvsection{Technical Skills}
\cventry{Operating Systems}{%
	Linux\sep macOS\sep Windows
}%
\cventry{Programming Languages}{%
	Python\sep C\sep C\ensuremath{++}\sep Java\sep MATLAB
}%
\cventry{Software Development Tools}{%
	Git\sep GitHub\sep GitLab
}%
\cventry{Simulation and Analysis Software}{%
	Ansys\sep Siemens Simcenter\sep MATLAB Simulink
}%
\cventry{Languages}{%
	English (Fluent)\sep German (Intermediate)
}

\cvsection{Personal Interests}
\cventry{Sports}{%
	Rock Climbing\sep Skiing\sep Cycling
}%
\cventry{Hobbies}{%
	Photography\sep Open-Source Contributions
}

\end{document}
